---
title: "SSaintFortLiveSession9HW"
author: "Salnave Saint-Fort"
date: "July 20, 2016"
output: html_document
---

## Salnave Saint-Fort
## MSDC 6306 Doing Data Science - 404
## Summer 2016
## SSaintFortLiveSession9HW


## Question 1

## Installing fpp package 
```{r loading ffp library}
library(fpp)
```
## Code to load data
```{r loading ukcars dataset}
data(ukcars)
```
## Plot the time series. Can you identify seasonal fluctuations and/or a trend? 
```{r}
plot(ukcars, main  = "Plot of ukcars dataset.")
```
## Use a classical decomposition to calculate the trend-cycle and seasonal indices. 
```{r}
fitd <- decompose(ukcars)
plot(fitd)
```

## Do the results support the graphical interpretation from part (a)? 
+ Answer:  Yes

## Compute and plot the seasonally adjusted data. 
```{r}
eeadj <- seasadj(fitd)
plot(eeadj, main = "Plot of Seasonally adjuted data")
```

## Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier? 
```{r}
ukcars2 <- ts(c(ukcars[1:54],ukcars[55]+500,ukcars[56:113]),start=c(1978,1),frequency=12)
plot(ukcars2, main= "Plot of ukcars with outlier near the middle of the dataset")

ukcars3 <- ts(c(ukcars[1:110],ukcars[111]+500,ukcars[112:113]),start=c(1978,1),frequency=12)
plot(ukcars3, main = "Plot of ukcars with outlier near the end of the dataset")
```
## Does it make any difference if the outlier is near the end rather than in the middle of the time series? 
+ Answer: Yes it makes a difference if the outlier is near the end rather than in the middle of the time series.

##	Use STL to decompose the series.
```{r}
fit <- stl(ukcars, s.window=5)

plot(fit, main = "Plot of Seasonal Trend Decomposition of ukcars dataset.")

plot(ukcars, col="gray",
     main="Plot of ukcars dataset with STL",
     ylab="New orders index", xlab="")
lines(fit$time.series[,2],col="red",ylab="Trend")
```
## Question 2

##loading the tseries package
```{r}
library(tseries)
```
## Getting the historical data for my assigned Stock "PEN"
```{r}
SNPdata <- get.hist.quote('PEN',quote="Close")
```

##	Calculate log returns.
```{r}
SNPret <- log(lag(SNPdata)) - log(SNPdata)
```
## Calculate volatility measure
```{r}
SNPvol <- sd(SNPret) * sqrt(250) * 100
SNPvol
```
## volatility 
```{r}
Vol <- function(d, logrets)
{
  
  var = 0
  
  lam = 0
  
  varlist <- c()
  
  for (r in logrets) {
    
    lam = lam*(1 - 1/d) + 1
    
    var = (1 - 1/lam)*var + (1/lam)*r^2
    
    varlist <- c(varlist, var)
    
  }
  
  sqrt(varlist)
}
```

## Calculate volatility measure with a continuous loopback window
```{r}
volest <- Vol(10,SNPret)

volest2 <- Vol(30,SNPret)

volest3 <- Vol(100,SNPret)

plot(volest,type="l", main="Plot of volitility measure with continous loopback")

lines(volest2,type="l",col="red")

lines(volest3, type = "l", col="blue")
```
